Physical Chemistry Tips

### 2015-12-06 physical_chemistry/latex/pchem_tips.tex
Adding everything.

\usepackage{amsmath}
\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

@@

\section{Random relationships}

\subsection{Weird unknown axioms}

\begin{align*}
  \frac{dH}{dP}_t &= -T\frac{dV}{dT}_P + V\\
\end{align*}

@@

>>>>

\usepackage{amsmath}
\usepackage{gensymb}
\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

@@

\section{Equations}
\begin{align*}
  \left(\frac{dU}{dV}\right)_T &= T\left(\frac{dP}{dT}\right)_V - P\\
  \left(\frac{dH}{dP}\right)_T &= -T\left(\frac{dV}{dT}\right)_P + V\\
  &\mbox{Arrived at via first law, expanding}\\
  &\mbox{a differential and a Maxwell relation}\\
\end{align*}

\begin{align*}
  \frac{d\left(\frac{G}{T}\right)}{dT} &= -\frac{H}{T^2}\\
\end{align*}

\begin{align*}
  H &= -T^2\left(\frac{\partial\left(G/T\right)}{\partial T}\right)_P
\end{align*}

\begin{align*}
  \kappa &= -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_T \hspace{1cm} \mbox{Cubic expansion}\\
\alpha &= \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_P \hspace{1cm} \mbox{Cubic expansion}\\
\end{align*}

\begin{align*}
  \left(\frac{\partial U}{\partial V}\right)_T &= \left(\frac{\partial H}{\partial P}\right)_T = 0\\
  \left(\frac{\partial U}{\partial T}\right)_V &= C_V \hspace{1cm} \mbox{For an ideal gas}\\
\end{align*}

@@

\begin{align*}
  \frac{\partial G}{\partial P}_T &= V\\
  \Delta \overline{G}_{ideal} &= \Delta G_{ideal}\degree + RT\ln\left(\frac{P}{P\degree}\right)\\
  \Delta \overline{G} &= \Delta G\degree + RT\ln\left(\frac{f}{P\degree}\right)\\
  \frac{f}{P} &= e^{\frac{1}{RT}\int_0^P(\bar{V}-\bar{V}^{id})dP} = e^{\int_0^P\frac{Z-1}{P}dP}\\
  \mu_i &= \mu_i\degree + RT\ln(a_i)\\
  \mu_i &= \mu_i\degree + RT\ln\left(\frac{f_i}{P\degree}\right)\\
\end{align*}

\begin{align*}
  K &= \Pi a_{i,eq}^{\nu_i}\\
  Q &= \Pi a_{i}^{\nu_i}\\
  K &= e^{\frac{-\Delta_r G\degree}{RT}}\\
  K_{gas} &= \Pi\left(\frac{f_{i,eq}}{P\degree}\right)^{\nu_i}\\
  K_{gas,ideal} &= \Pi\left(\frac{P_{i,eq,ideal}}{P\degree}\right)^{\nu_i}\\
\end{align*}
Equilibrium constant. The product of all the concentrations of the reaction. At standard state, the Gibbs free energy is $\sum \mu_i\degree\nu_i$.

\begin{align*}
  P_i &= \frac{n_iRT}{V} = C_iRT\\
  K_p &= \Pi \left(\frac{C_iRT}{P\degree}\right)^{\nu_i} = \left(\frac{C_i\degree RT}{P\degree}\right)^{\nu_i} \Pi \left(\frac{C_i}{C_i\degree}\right)^{\nu_i}\\
\end{align*}

\begin{align*}
  \mbox{Ideal gas expansion}&\hspace{2cm}\Delta S = R\ln(\frac{V_2}{V_1})\\
  \mbox{Ideal gas mixing}&\hspace{2cm}\Delta S = -R\sum y_i\ln(y_i)\\
  \mbox{Nonideal phase transition}&\hspace{2cm} \Delta S = \frac{\Delta H}{T}\\
\end{align*}

\begin{align*}
  \mbox{Boltzmann Hypothesis}&\hspace{2cm} S = k\ln(\Omega)\\
\end{align*}

\begin{align*}
  \mbox{Second law of thermodynamics}&\hspace{2cm} dS \geq \frac{dQ_{rev}}{T}\\
  \mbox{Third law of thermodynamics}&\hspace{2cm}\mbox{Crystals have zero entropy}\\
\end{align*}

\begin{align*}
  \mbox{Carnot cycle}&\hspace{2cm}\eta = \frac{w}{q_1} = \frac{\Delta T}{T_1}\\
\end{align*}

\begin{align*}
  \mu_i = \mu_i\degree + RT\ln\left(\frac{P_i}{P\degree}\right)\\
  \overline{G}_i = \overline{G}_i\degree + RT\ln\left(\frac{P_i}{P\degree}\right)\\
\end{align*}

\section{Things to know}
\begin{align*}
  &\mbox{Prove entropy is exact for both ideal and nonideal gasses}\\
  &\mbox{Derive first relations in document, the ones with dU/dV}\\
\end{align*}
